### 2022-07-25 sections/introduction.tex
updates plots labels
minor updates

The study of $pp\rightarrow tH$ processes will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.

@@

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis reported here targets Higgs boson decays into 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons in the complete Run~2 dataset collected by ATLAS in 2015--2018. The corresponding integrated luminosity is 139 fb$^{-1}$. Both $\ttbar \to WbHq$ decays and $pp \to tH$ production are sought. The dataset is divided into several final states depending on the production mode and
the  $W$ boson and $\tau$-lepton decays. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are denoted by $t_h$ ($t_{\ell}$).
The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are denoted by $\lep$, while the decays $\tau \to \text{hadrons} + \nu_{\tau}$ are denoted by $\thad$.
The contribution of 
$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$-lepton decays into a light lepton (electron or muon) or as $\thad$ 
in $t_h$ when the $\tau$-lepton decays hadronically.
%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either the $\tlhad$ or $\thadhad$ final state when the top quark decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
when the top quark decays leptonically ($t_{\ell}$), in order to avoid overlaps with
other ATLAS searches~\cite{Aaboud:2018pob}. 
In this search, events with two hadronically decaying $\tau$-leptons and no electron or muon define the hadronic channel. Events with at least one \tauhad and an additional electron or muon (corresponding to $t_{\ell}$ or $\lep$ events) are assigned to leptonic channels. More signal regions (with the top quark decaying leptonically) are exploited here than in the previous FCNC $\Htautau$ search, which was conducted using the partial Run~2 dataset~\cite{fcnc36}.
In addition, an improved treatment of misidentified $\tau$-leptons (`fakes') in simulation and in data-driven
estimations of fakes from multi-jet background is implemented.
% and more
%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique based on boosted decision trees is used to discriminate between the signal and the background on the basis of their different kinematical distributions.

>>>>

The study of $pp\rightarrow tH$ processes will also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.

@@

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis reported here targets Higgs boson decays into 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons in the complete Run~2 dataset collected by ATLAS in 2015--2018. The corresponding integrated luminosity is 139 fb$^{-1}$. Both $\ttbar \to WbHq$ decays and $pp \to tH$ production are sought. The dataset is divided into several final states depending on the production mode and
the  $W$ boson and $\tau$-lepton decays. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are denoted by $t_h$ ($t_{\ell}$).
The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are denoted by $\lep$, while the decays $\tau \to \text{hadrons} + \nu_{\tau}$ are denoted by $\thad$.
The contribution of 
$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$-lepton decays into a light lepton (electron or muon) or as $\thad$ 
in $t_h$ when the $\tau$-lepton decays hadronically.
%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either the $\tlhad$ or $\thadhad$ final states when the top quark decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
when the top quark decays leptonically ($t_{\ell}$), in order to avoid overlaps with
other ATLAS searches~\cite{Aaboud:2018pob}. 
In this search, events with two hadronically decaying $\tau$-leptons and no electron or muon define the hadronic channel. Events with at least one \tauhad and an additional electron or muon (corresponding to $t_{\ell}$ or $\lep$ events) are assigned to leptonic channels. More signal regions (with the top quark decaying leptonically) are exploited here than in the previous FCNC $\Htautau$ search, which was conducted using the partial Run~2 dataset~\cite{fcnc36}.
In addition, an improved treatment of misidentified $\tau$-leptons (`fakes') in simulation and in data-driven
estimations of fakes from multi-jet background is implemented.
% and more
%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique based on boosted decision trees is used to discriminate between the signal and the background on the basis of their different kinematical distributions.

### 2022-07-25 sections/objects.tex
minor updates

Electron candidates~\cite{EGAM-2018-01} are reconstructed from energy 
clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;
electron candidates in the transition region between the EM barrel and endcap calorimeters 
($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy `tight' likelihood-based identification 
criteria~\cite{PERF-2016-01}
%~\cite{ATLAS-CONF-2016-024}
based on calorimeter, tracking and combined variables that provide 
separation between electrons and jets.

@@

`Tight' isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions by using a trained isolation boosted decision tree (BDT)
\texttt{PromptLeptonVeto} (PLIV), which identifies non-prompt light leptons by using lifetime information associated with a track-jet that matches the selected light lepton.
%~\cite{ATLAS-CONF-2019-045}.
These additional reconstructed charged-particle tracks inside the jet can be
used to increase the efficiency for identifying the displaced decay vertices of heavy-flavour ($b$, $c$) hadrons that produced non-prompt leptons.
The `tight' working points are used for leptons with high $\pt$ ($>20~\GeV$).
Simulation-to-data scale factors for the efficiencies of the `tight' PLIV working points are measured using the tag-and-probe method~\cite{PERF-2016-01}
with $Z\rightarrow \ell^+\ell^-$ events. These scale factors were checked for electrons or muons from the $\tau$-lepton decays
using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, and are consistent at the 2\% level. To be conservative, an
additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the $\tau$-lepton in the lepton+$\thad$ channels.
%Additionally, the $\Htautau$ search requires leptons to
%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
%percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

>>>>

Electron candidates~\cite{EGAM-2018-01} are reconstructed from energy 
clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;
electron candidates in the transition region between the EM barrel and endcap calorimeters 
($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy `tight' likelihood-based identification 
criteria~\cite{PERF-2017-01}
%~\cite{ATLAS-CONF-2016-024}
based on calorimeter, tracking and combined variables that provide 
separation between electrons and jets.

@@

`Tight' isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions by using a trained isolation boosted decision tree (BDT)
\texttt{PromptLeptonVeto} (PLIV), which identifies non-prompt light leptons by using lifetime information associated with a track-jet that matches the selected light lepton.
%~\cite{ATLAS-CONF-2019-045}.
These additional reconstructed charged-particle tracks inside the jet can be
used to increase the efficiency for identifying the displaced decay vertices of heavy-flavour ($b$, $c$) hadrons that produced non-prompt leptons.
The `tight' working points are used for leptons with high $\pt$ ($>20~\GeV$).
Simulation-to-data scale factors for the efficiencies of the `tight' PLIV working points are measured using the tag-and-probe method~\cite{PERF-2017-01}
with $Z\rightarrow \ell^+\ell^-$ events. These scale factors were checked for electrons or muons from the $\tau$-lepton decays
using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, and are consistent at the 2\% level. To be conservative, an
additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the $\tau$-lepton in the lepton+$\thad$ channels.
%Additionally, the $\Htautau$ search requires leptons to
%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
%percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

### 2022-07-25 sections/systematic_uncertainties.tex
minor updates

Uncertainties associated with electrons, muons, and $\had$ candidates arise from the trigger, reconstruction,  
identification and, in the case of electrons and muons, isolation efficiencies, as well as the momentum scale and resolution. 
These are measured using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{PERF-2016-01,Aad:2016jkr} 
in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\had$ candidates~\cite{ATLAS-CONF-2017-029}.

>>>>

Uncertainties associated with electrons, muons, and $\had$ candidates arise from the trigger, reconstruction,  
identification and, in the case of electrons and muons, isolation efficiencies, as well as the momentum scale and resolution. 
These are measured using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{PERF-2017-01,Aad:2016jkr} 
in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\had$ candidates~\cite{ATLAS-CONF-2017-029}.
